Graphs, partitioning and you

### 2016-01-31 evolutionaryComputation/2-practical/report.tex
added about building

>>>>

\subsection{Build tool}
I use Gradle for building the project. Its the most advanced build platform
available and makes it easy to add dependencies to the project.
For example I use slf4j for logging.

Its also handy in that it comes with a self installing script that can be run
from any platform, Gradlew. So running the code I wrote on a different machine
becomes easy, Gradle makes sure the right dependencies are fetched.

\paragraph{Running it}

Open a shell and move to the project folder then type:

\lstset{language=Bash}
\begin{lstlisting}[frame=single]
	./gradlew run
\end{lstlisting}

\subsection{Libraries used}
In here I will describe why I chose to use these libraries
The details of the libraries can be found in the Gradle file (which
version and what maven group):

\begin{lstlisting}[frame=single]
	cat code/build.gradle
\end{lstlisting}

\begin{itemize}
	\item The Scala standard library, because I have to when using Scala.
	\item slf4j, a simple logging facade, this allows runtime switching of
		logging schemes, for example if you want to log into a database or
		a file instead of stdout you can do this relatively easy with slf4j
		This is not necessary right now but the API is simple enough to use
		everywhere.
	\item Scalaplot. A graph plotting library for Scala. I didn't want to
		do this myself, and this library supports SVG plotting and ASCII
		plotting.
	\item Scalatest. A testing library for Scala, it has some pretty advanced
		features but I use it mostly like JUnit.
	\item appache commons math: For the statistics calculations.
\end{itemize}
